Conflict Driven Evolution and Urban Development: \\ Evidence from the Holy Roman Empire\footnote{ I thank Lara Andermann, Leonie Bielefeld, Daniel Bursian, Davide Cantoni, Emilio Esguerra, Filip Milojevic, Johannes Vorbach and Matthias Weigand for helpful comments and feedback. }

### 2023-06-27 paper/paper.tex
#31 first third of conclusion

@@

Improvements / future research:
\begin{itemize}
    \item differences in timing - do early switchers in my sample experience different effects than late switchers?
    \item further explore differences across regions
    \item better measures of state power
\end{itemize}

>>>>

Early modern Europe was a uniquely warlike place. A recent theory models wars and conflict as a Darwinian selection mechanism: strong states absorb the territory of weak ones, which gradually filters out weaker states. If this is true, territory that changes hands during conflict will generally tend to move into the possession of a stronger state and benefit from its strength.

In this paper I test this prediction of the theory in the setting of the Holy Roman Empire. I want to understand the role that the process of conflict-driven evolution played in the economic development of Europe. I use data compiled from an encyclopedia of 2,390 historically German cities, covering the years 1300 to 1800. I use records of construction activity as a proxy for economic activity on the city level.

I run panel regressions with two-way fixed effects and staggered adoption on this dataset. First I estimate the dynamic effects of switching to another state. A significant effect manifests one century after a switch and becomes larger over time; after two centuries, we are 9 percentage points more likely to observe construction in cities that switched states.

I then estimate heterogeneous treatment effects of different types of switches. In particular, I care about the difference between the treatment effect of conquests and the treatment effect of successions: if we assume that conquests are more strongly associated with state power than successions, then we can interpret a switch by conquests as a proxy for an increase in state power.

@@

One could do more to explore the idiosyncrasies of the setting. 
Improvements / future research:
\begin{itemize}
    \item differences in timing - do early switchers in my sample experience different effects than late switchers?
    \item further explore differences across regions
    \item better measures of state power
\end{itemize}
